--- 
title: "BIO-2002 | Bioinformatique"
author: "XXX"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---
`r if (knitr:::is_html_output()) '
# Bienvenue {-}
'`
XXX

`r if (knitr:::is_html_output()) '
# Introduction à Benchling {-}
'`
<!-- <iframe src="https://docs.google.com/presentation/d/e/2PACX-1vTv1D_QDTvZbROVZpkNiZx2Tf9ORSo8gfovNMrlB7Av8I_nTv--MczSm00QW4vtJQ/embed?start=false&loop=false&delayms=2000" frameborder="0" width="600" height="366" allowfullscreen="true" mozallowfullscreen="true" webkitallowfullscreen="true"></iframe> -->

`r if (knitr:::is_html_output()) '
# XXX {-}
'`
XXX

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
